An Air Drop That Preserves Recipient Privacy

### 2019-01-07 paper.tex
edits

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
%and write $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$
set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
% \left(\begin{array}{l}
% Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
% Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
% Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
% Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
% Z_5 \gets \lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{na})/\ell \rfloor 
% \end{array}\right) \in \GG^4 \times \ZZ$, \AlgSep
compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that $c_1, c_2, \Rv, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell$ and $\Zv_q$. 
In an interaction with a real prover 
the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
Consider one value $r \rgets \range{2^{2\lambda}}$.
Because $2^{2\lambda}$ is much larger than $\ell$
we know that the pair 
$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
It directly follows that $\zv_\ell$ is statistically close to uniform 
in $\range{\ell}^8$, as in the simulation.
It remains to argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Let's start with the last component of~$\Zv_q$, namely $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$ we have
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1, \pm 2\}$. 
Hence, because in the real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the simulation, 
this $Z_5$ is distributed 
statistically close to its distribution in the simulation.
Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
{\bf TODO:} explain why.
\end{proof}

>>>>

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randv}
\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover 
the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
Consider one value $r \rgets \range{2^{2\lambda}}$.
Because $2^{2\lambda}$ is much larger than $\ell$
we know that the pair 
$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in the simulation.

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
Then the simulated $\Zv_q$ is computed as:
\begin{equation} \label{eq:sim}
\Zv_q \deq \left(\begin{array}{l}
Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
\end{array}\right) \in \GG^4 \times \ZZ.  
\end{equation}
Let's start with $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ is a real transcript satifies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1, \pm 2\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the the simulated $Z_5$ in~\eqref{eq:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
Because $\Delta$ is small, $\Delta \in \{0, \pm 1, \pm 2\}$,
this difference only negligibly affects the statistical distance. 
We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
is statistically close to its real distribution.
Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
{\bf TODO:} explain why.

Finally, it is not difficult to see that the computed $\Rv$ 
on line~\eqref{ln:computeR} is, with overwhelming probability,
the image under $\phi$ of some element $\rv' \in \range{2^{2\lambda}}^8$,
as in a real transcript.
{\bf TODO:} explain why.
\end{proof}
